Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Text and Figures to Instrumented NC Wall Section

\chapter{Instrumented Calibration (non-combustible) Wall Experiments}
Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.  In these experiments the target is a non-combustible wall and therefore the wall will not contribute to the fire.  The fires were initially placed at predetermined, fixed positions away from the wall.  In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel. Starting at a position where the closest edge of the burner was two burner widths from the wall. The burner was moved toward the wall until the burner was against the wall.

\section{Experimental Arrangement}
A free standing steel frame wall with a 12.7 mm thick, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.

@@

>>>>

\chapter{Instrumented Calibration (non-combustible) Wall Experiments}
Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.  In these experiments the target is a non-combustible wall. The non-combustible material was chosen to eliminate any contribution from the wall to the fire.  The fires were initially placed at predetermined, fixed positions away from the wall.  In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel. Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610 m), one burner width (0.305 m), one half burner width (0.150 m), and the touching the wall.

\section{Experimental Arrangement}
A free standing steel frame wall with a 12.7 mm thick, 2.44 m high by 1.22 m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2 m to 1.2 m above the burner.  One vertical array was centered on the burner and the other vertical array was centered on the right edge of the burner. The arrangement is shown in Fig.~\ref{Instrumented_NC_Wall}. Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20 cm intervals, up to a height of 2.2 m above the surface of the burner. Photographs of the front and rear of the instrumented wall are shown in Figures~{Instrumented_Wall_Front_photo,Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.  The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall. The photograph in Figure~{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Rear_photo}\\
	\caption[Photograph of the rear side of the instrumented non-combustible wall]{Photograph of the rear side of the instrumented non-combustible wall.}
	\label{Instrumented_Wall_Rear_photo}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Close_up_TC_HF_photo}\\
	\caption[Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.]{Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.}
	\label{Instrumented_Wall_Close_up_TC_HF_photo}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Detail_Rear_TC_photo}\\
	\caption[Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall]{Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall.}
	\label{Instrumented_Wall_Detail_Rear_TC_photo}
\end{figure}
